Supplementary materials

### 2018-02-22 publication/supp_info.Rmd
Calculate abundances and phenology overlap

>>>>

```{r abundance logtransformed or not, fig.height = 3, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}
loadd(plant_rel_abu, sites)

p1 <- plant_rel_abu %>%
  inner_join(sites, by = 'site_name') %>%
  ggplot() +
  stat_density(aes(x = abu_com_rel_log, colour = locality_name),
               position = position_identity(), geom = 'line') +
  # stat_density(aes(x = abu_tot_rel_log), geom = 'line') +
  scale_color_brewer(palette = "Set1") +
  pub_theme() +
  # guides(colour = guide_legend(title = 'locality'), linetype = guide_legend(title = 'land use')) +
  labs(colour = 'locality', x = 'relative abundance')

p2 <- plant_rel_abu %>%
  inner_join(sites, by = 'site_name') %>%
  ggplot(aes(x = abu_tot)) +
  stat_density(position = position_identity(), geom = 'line') +
  scale_color_brewer(palette = "Set1") +
  pub_theme() +
  labs(x = 'abundance (floral units)')

cowplot::plot_grid(p2, p1, rel_widths = c(0.42, 0.58), labels = LETTERS[1:2], label_size = 8)
